SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 back.tex
Condensing for space, Coverage and CrossVal Images

\noindent \textbf{Confidence Tracking}: As shown in
figure~\ref{fig:spp_structure}, the Pattern Table keeps a count of
hits to each signature through a counter C\textsubscript{sig}. The
number of hits for a given delta per signature are tracked using a
counter C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a
demand hit to the number of prefetches recommended in total. The range
of $\alpha$ is [0,1].  $D$ is the lookahead depth. For $d = 1$, when
SPP is in non-speculative mode, P\textsubscript{0} can be thought of
as 1.  The final P\textsubscript{d} is thresholded against prefetch
threshold (T\textsubscript{p}) to reject the low confidence
suggestions and then against a numerically bigger fill threshold
(T\textsubscript{f}) to decide whether the prefetch should be sent to
L2 Cache (high confidence prefetch) or Last Level Cache (low
confidence prefetch).  The two thresholds were empirically set to 25
and 90 respectively, on the scale of 0 to 100.

>>>>

\noindent \textbf{Confidence Tracking}: As shown in
figure~\ref{fig:spp_structure}, the Pattern Table keeps a count of
hits to each signature through a counter C\textsubscript{sig}. The
number of hits for a given delta per signature are tracked using a
counter C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a
demand hit to the number of prefetches recommended in total. The range
of $\alpha$ is [0,1].  $D$ is the lookahead depth. For $d = 1$, when
SPP is in non-speculative mode, P\textsubscript{0} can be thought of
as 1.  The final P\textsubscript{d} is thresholded against prefetch
threshold (T\textsubscript{p}) to reject the low confidence
suggestions and then against a numerically bigger fill threshold
(T\textsubscript{f}) to decide whether to send the prefetch to
L2 Cache (high confidence prefetch) or Last Level Cache (low
confidence prefetch). The two thresholds were empirically set to 25
and 90 respectively, on the scale of 0 to 100.

### 2018-12-07 results.tex
Condensing for space, Coverage and CrossVal Images

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on one of the
{\tt 602.gcc\_s} traces. This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher for that trace -- BOP. In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt 623. xalancbmk\_s} and {\tt
649.fotonik3d\_s} benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better 
than the next best prefetcher -- SPP.\\ \\
%
\begin{figure}[h]
\includegraphics[width=\columnwidth]{Coverage}
\caption{Fraction of Cache Misses Covered}
\label{Fig:Coverage}
\end{figure}
%
% djimenez: this is a weird way to make a header for a section. use \paragraph or \subsection
\noindent \textbf{Coverage:}
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

\begin{figure}[ht]
\includegraphics[width=0.8\columnwidth,height=4cm,keepaspectratio]{SPEC2006}
\caption{SPEC CPU 2006 Single-Core IPC Speedup}
\label{Fig:SPEC2006_1core}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.9\columnwidth,height=3.5cm,keepaspectratio]{CloudSuite}
\caption{IPC Speedup for CloudSuite Workloads}
\label{Fig:CloudSuite}
\end{figure}

%% \begin{figure}[ht]
%%   \centering
%%   \begin{subfigure}{0.5\columnwidth}
%%     \centering
%%     \includegraphics[width=0.45\columnwidth]{CloudSuite}
%%     \caption{CloudSuite Workloads}
%%   \end{subfigure}
%%   %
%%   \begin{subfigure}{0.5\columnwidth}
%%     \centering
%%     \includegraphics[width=0.45\columnwidth]{SPEC2006}
%%     \caption{Single Core SPEC CPU 2006}
%%   \end{subfigure}
%%   \caption{Performance with Unseen Benchmarks}
%%   \label{Fig:CrossVal}
%% \end{figure}

@@

Figure~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and
PPF on the memory intensive subset and the full SPEC CPU 2006 suite. 
PPF provides a speedup of \textbf{36.3\%} over the baseline on the 
memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an improvement 
of \textbf{3.33\%} over SPP.

@@

Figure~\ref{Fig:CloudSuite} shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.78\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.

>>>>

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on one of the
{\tt 602.gcc\_s} traces. This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher for that trace -- BOP. In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt {623.xalancbmk}\_s}~~and~~{\tt
649.fotonik3d\_s}  benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better 
than the next best prefetcher -- SPP.\\ \\
%
\begin{figure}[ht]
\includegraphics[width=\columnwidth]{Coverage}
\caption{Fraction of Cache Misses Covered}
\label{Fig:Coverage}
\end{figure}
%
% djimenez: this is a weird way to make a header for a section. use \paragraph or \subsection
\noindent \textbf{Coverage:}
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

%% \begin{figure}[ht]
%% \includegraphics[width=0.8\columnwidth,height=4cm,keepaspectratio]{SPEC2006}
%% \caption{SPEC CPU 2006 Single-Core IPC Speedup}
%% \label{Fig:SPEC2006_1core}
%% \end{figure}
%% 
%% \begin{figure}[ht]
%% \includegraphics[width=0.9\columnwidth,height=3.5cm,keepaspectratio]{CloudSuite}
%% \caption{IPC Speedup for CloudSuite Workloads}
%% \label{Fig:CloudSuite}
%% \end{figure}

\begin{figure}[ht]
\begin{adjustwidth}{-0.4cm}{}
\includegraphics[width=1.1\columnwidth]{CrossVal}
\caption{IPC Speedup for Unseen Workloads}
\label{Fig:CrossVal}
\end{adjustwidth}
\end{figure}

@@

Figure~\ref{Fig:CrossVal}(a) shows the speed-up achieved by BOP, SPP and
PPF on the memory intensive subset and the full SPEC CPU 2006 suite for a
single-processor machine. 
PPF provides a speedup of \textbf{36.3\%} over the baseline on the 
memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an improvement 
of \textbf{3.33\%} over SPP.

@@

Figure~\ref{Fig:CrossVal}(b) shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.78\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.
